Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602

### 2020-07-14 paper/ms.tex
add da figure

\input{starparams.tex}

@@

\input{model_posterior_table.tex}

@@

\tn\ joins a number of other young planetary systems reported from
TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
\citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
Unlike these planets, \pn\ is validated but not yet confirmed.

@@

The maximum amplitude of the Rossiter-McLaughlin anomaly is
\citep{gaudi_prospects_2007}
\begin{align}
  \Delta V_{\rm RM} &\approx f_{\rm LD} \cdot \delta \cdot v\sin i \cdot \sqrt{1-b^2}
  \approx 14\,{\rm m\,s}^{-1},
\end{align}
for
\begin{align}
  f_{\rm LD} &= 1 - c_1 ( 1 - \mu ) - c_2 (1 - \mu )^2,
\end{align}
where $\mu \approx (1 - b^2)^{1/2}$, and for calculation purposes we
assumed $b=0.95$ and used stellar and transit parameters from
Tables~\ref{tab:starparams} and~\ref{tab:posterior}.  Although
challenging, for a 1.9$\,$hr transit of a $V=10.6$ star, a detection
could be achieved with modern spectrographs.  The next viable total
transit windows from Chile occur in January and February of 2021;
there are also a few visible per season from other southern locations.
The most precise available ephemeris, found from our joint fit of the
TESS and ground-based photometry, is as follows.
\begin{align}
  t_0\ [{\rm BJD_{TDB}}] &= 2458574.272529 \pm 0.000587 \nonumber \\
  P\ [{\rm d}] &= 8.3248764 \pm 0.0000155 \nonumber \\
  T_{14}\ [{\rm hr}] &= 1.86 \pm 0.04.
\end{align}

@@

% \clearpage

@@

%\clearpage
\acknowledgements
\tn\ was included on the TESS ``short-cadence'' target list in part
thanks to the Guest Investigator program of G.\ Sacco (G011265).
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We acknowledge support from the French and Italian Polar Agencies, IPEV and PNRA, and from Universit\'e C\^ote d’Azur under Idex UCAJEDI (ANR-15-IDEX-01). We thank the dedicated staff at Concordia for their continuous presence and support throughout the Austral winter.
%
This research received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement n$^\circ$ 803193/BEBOP), and from the Science and Technology Facilities Council (STFC; grant n$^\circ$ ST/S00193X/1).
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%
This research made use of the Exoplanet Follow-up Observation
Program website, which is operated by the California Institute of
Technology, under contract with the National Aeronautics and Space
Administration under the Exoplanet Exploration Program.
%
This research has made use of the SVO Filter Profile Service
(\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
MINECO through grant AYA2017-84089.
%
%
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%

@@

% \input{ic2602_ages.tex}
% \input{starparams.tex}
% \input{model_posterior_table.tex}
% \input{TOI837_phot_table.tex}
% \input{TOI837_rv_table.tex}

>>>>

%\input{starparams.tex}

@@

%\input{model_posterior_table.tex}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Planet radius versus age, for the known transiting planets.} 
    Systems younger than 100$\,$Myr are emphasized.  Ages and radii
    were queried from the NASA Exoplanet Archive on 13 July 2020.
    Precise ages are known for only a small fraction of the gray points.
		\label{fig:rpvsage}
	}
\end{figure}

\tn\ joins a number of other young planetary systems reported from
TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
\citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
Figure~\ref{fig:rpvsage} shows \tn\ in the space of planets sizes and ages.
\tn\ is among the youngest transiting planets known, which was the
primary motivation for this study.
While we have statistically validated that \tn\ seems to be a planet,
the possibility that it is a background eclipsing binary has not
been excluded with sufficient confidence to call the planet ``confirmed''.

@@

The maximum amplitude of the Rossiter-McLaughlin anomaly is
\citep{gaudi_prospects_2007}
\begin{align}
  \Delta V_{\rm RM} &\approx f_{\rm LD} \cdot \delta \cdot v\sin i \cdot \sqrt{1-b^2}
  \approx 14\,{\rm m\,s}^{-1},
\end{align}
for
\begin{align}
  f_{\rm LD} &= 1 - c_1 ( 1 - \mu ) - c_2 (1 - \mu )^2,
\end{align}
where $\mu \approx (1 - b^2)^{1/2}$, and for calculation purposes we
assumed $b=0.95$ and used stellar and transit parameters from
Tables~\ref{tab:starparams} and~\ref{tab:posterior}.  Although
challenging, for a 1.9$\,$hr transit of a $V=10.6$ star, a detection
could be achieved with modern spectrographs.  The next viable total
transit windows from Chile occur in January and February of 2021;
there are also a few visible per season from other southern locations.
The most precise available ephemeris, found from our joint fit of the
TESS and ground-based photometry, is as follows.
\begin{align}
  t_0\ [{\rm BJD_{TDB}}] &= 2458574.272523 \pm 0.000594 \nonumber \\
  P\ [{\rm d}] &= 8.3248762 \pm 0.0000156 \nonumber \\
  T_{14}\ [{\rm hr}] &= 1.86 \pm 0.04.
\end{align}
% /Users/luke/Dropbox/proj/timmy/results/TOI_837_allindivtransit_phot_results/20200711/posterior_table_clean_allindivtransit.tex

@@

@@

\clearpage
\acknowledgements
\tn\ was included on the TESS ``short-cadence'' target list in part
thanks to the Guest Investigator program of G.\ Sacco (G011265).
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We acknowledge support from the French and Italian Polar Agencies, IPEV and PNRA, and from Universit\'e C\^ote d’Azur under Idex UCAJEDI (ANR-15-IDEX-01). We thank the dedicated staff at Concordia for their continuous presence and support throughout the Austral winter.
%
This research received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement n$^\circ$ 803193/BEBOP), and from the Science and Technology Facilities Council (STFC; grant n$^\circ$ ST/S00193X/1).
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%
This research made use of the Exoplanet Follow-up Observation
Program website, which is operated by the California Institute of
Technology, under contract with the National Aeronautics and Space
Administration under the Exoplanet Exploration Program.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This research has made use of the SVO Filter Profile Service
(\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
MINECO through grant AYA2017-84089.
%
%
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%

@@

% \input{TOI837_phot_table.tex}
% \input{TOI837_rv_table.tex}
% \input{ic2602_ages.tex}
\input{starparams.tex}
\input{model_posterior_table.tex}
